---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 

Write a function that given your birthday (as a date), returns how old you are in years.

Write a function that given your birthday, returns the day of the week you were born on.


```{r}

library(tidyverse)

library(lubridate)
library(nycflights13)


Current_Year <- years(2019) + months(c(1:12)) + days(1)

```


```{r}

# let x be my birthdate in the format year, month and day

currentAge <- function (birthday) {
  
  Age <- today() - ymd(birthday)
  
  as.numeric(as.duration(Age), "years") %/%1  
  
  
}

currentAge(19971205)

```



```{r}

dayofweek <- function (birthday) {
  birthday <- ymd(birthday)
  Day <- wday(birthday, label = TRUE, abbr = FALSE)
  
  Day
  
  
}

dayofweek(19970823)

```















## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r}
library(RVerbalExpressions)
library(tidyverse)
library(stringr)
allwords <- stringr::words

#  Regular Expressions

str_view(allwords,"^.......+", match = TRUE)

#Verbal Expressions

seven_and_more <- rx() %>% 
  rx_start_of_line() %>% 
  rx_alpha() %>% 
  rx_multiple(min = 7) 
  
  allwords[str_detect(allwords,seven_and_more)]



```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)



```{r}
allwords <- stringr::words

# Regular Expressions

allwords[str_detect(allwords,"[aeiouAEIOU]",negate = TRUE)]

# Verbal Expressions

NotVowels <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but("aeiou") %>% 
  rx_multiple(min = 1) %>% 
  rx_end_of_line()

allwords[str_detect(allwords, NotVowels)]

```

Empirically verify the rule “i before e except after c”


```{r}

#allwords[str_detect(allwords,"ie")]
# Regular Expressions

allwords[str_detect(allwords,"[^c]ie")]

# Verbal Expressions

ie_without_c <- rx() %>% 
  rx_avoid_prefix("c") %>% 
  rx_find("ie")
 

allwords[str_detect(allwords,ie_without_c)]
  



```



Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.


```{r}
telephone <- c("217-377-2867", "217.377.2867", "EM7.377.2867" )

# Rehular Expressions

str_view(telephone, "^\\d{3}[-\\.]\\d{3}[-\\.]\\d{4}$")

# Verbal Expressions

tel_verbal_expression <- rx() %>% 
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print() 

telephone[str_detect(telephone,tel_verbal_expression)]



```


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

